\input{_preamble.tex}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Alex Huaracha} \\ \vspace{1pt}
    \small
    \href{mailto:alexhuarachaq@gmail.com}{\underline{alexhuarachaq@gmail.com}}
    $|$
    \href{http://linkedin.com/in/alex-huaracha}{\underline{linkedin.com/in/alex-huaracha}} $|$
    \href{http://github.com/Alex-Huaracha}{\underline{github.com/Alex-Huaracha}}
    $|$
    \href{https://alexhuaracha.vercel.app/}{\underline{alexhuaracha.vercel.app/}}
\end{center}


%-----------EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Full Stack Software Developer}{Jan 2026 -- Present}
      {Transportes Hagemsa S.A.}{Arequipa, AQP}
      \resumeItemListStart
        \resumeItem{Led the Commercial module of an ERP (\textbf{NestJS, Next.js}) that replaced a manual Excel and Word process, \textbf{cutting quote and contract generation from about 30 to 5 minutes} through form autocompletion and price suggestions based on historical quotes, with automatic emailing of the PDFs to the client.}
        \resumeItem{Implemented the module as an independent microservice under \textbf{DDD}, propagating data to dependent modules (Operations, Fleet, Business Partners) via \textbf{REST}, with \textbf{unit and e2e tests} and deployment to \textbf{Google Cloud with CI/CD}; discarded an \textbf{Apache Kafka} prototype due to operational costs.}
        \resumeItem{Built the complete vehicle maintenance management system (\textbf{Java/Spring Boot} backend and two \textbf{Flutter} apps) with \textbf{100+ active users} across 3 roles, digitizing work orders and the tracking of technicians' time and productivity.}
      \resumeItemListEnd

    \resumeSubheading
      {Artificial Intelligence Research Assistant}{May 2025 -- Jan 2026}
      {Universidad Nacional de San Agustin}{Arequipa, AQP}
      \resumeItemListStart
        \resumeItem{Built scalable data pipelines with \textbf{Python, TensorFlow, and Pandas}, processing over \textbf{32 million GPS records} for the public transport system.}
        \resumeItem{Designed Deep Learning models (\textbf{LSTM Autoencoders}) for anomaly detection, achieving a \textbf{53.7\% improvement} over traditional methods.}
      \resumeItemListEnd

    \resumeSubheading
      {Backend Development Intern}{Aug 2024 -- Jul 2025}
      {Universidad Nacional de San Agustin}{Arequipa, AQP}
      \resumeItemListStart
        \resumeItem{Built a REST API with \textbf{20+ endpoints} and a \textbf{multi-tenant} database schema for a requirements-engineering SaaS platform, enabling multiple organizations to manage projects in isolation with \textbf{Node.js, TypeScript, PostgreSQL, and Prisma ORM}.}
        \resumeItem{Implemented \textbf{JWT} authentication and \textbf{hierarchical RBAC} with 4 permission levels (admin, organization owner, project leader, member), ensuring isolation of sensitive data across organizations.}
        \resumeItem{Developed automated document-generation modules (\textbf{PDF and Excel}) and evidence management with file uploads, automating the software requirements lifecycle for development teams.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{E-commerce Microservices Platform} $|$ \emph{Node.js, TypeScript, Docker, Redis}}{Jul 2025 -- Nov 2025}
          \resumeItemListStart
            \resumeItem{Designed a scalable, containerized microservices architecture with \textbf{Docker}, orchestrating services behind a unified API Gateway.}
            \resumeItem{Implemented high-performance asynchronous task processing using an event-driven architecture with \textbf{Redis and Bull Queues}.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Gym Management SaaS System} $|$ \emph{Java, Spring Boot, PostgreSQL, Docker}}{Dec 2025 -- Feb 2026}
          \resumeItemListStart
            \resumeItem{Architected the backend with Spring Boot 3 and Java, applying design patterns (DTO, Repository) and \textbf{ACID} transactions to ensure integrity in membership and access management.}
            \resumeItem{Developed a \textbf{Business Intelligence} module using optimized \textbf{native SQL} and JPQL queries to compute financial \textbf{KPIs} and visualize attendance trends in real time.}
        \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Universidad Nacional de San Agustin}{Aug 2020 -- Jul 2025}
      {B.Sc. in Systems Engineering}{Arequipa, AQP}
      \resumeItemListStart
        \resumeItem{Coursework: Algorithms and Data Structures, Databases, Applied Machine Learning, Operating Systems, Software Engineering Practice.}
      \resumeItemListEnd
    \resumeSubheading
      {The Odin Project - Open Source }{Aug 2025 -- Dec 2025}
      {Full Stack Developer}{Remote}
        \resumeItemListStart
            \resumeItem{Completed 1000+ hours of hands-on development building full stack applications from scratch with \textbf{Node.js, React, and PostgreSQL}, applying \textbf{TDD} and RESTful API design.}
        \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: TypeScript, Python, Java, SQL (Postgres), JavaScript, HTML/CSS} \\
     \textbf{Frameworks}{: React, Next.js, Node.js, Nest.js, Spring Boot, Flutter, Hono, FastAPI, Vitest, TensorFlow, Pandas, ORM} \\
     \textbf{Tools}{: Git, Docker, Testcontainers, Redis, MySQL, Postman, JIRA, Google Cloud (GCP), Apache Kafka} \\
     \textbf{Languages (Spoken)}{: Spanish (Native), English (B2 - Upper Intermediate)} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
